% =============================================================================
% RESUME TEMPLATE
% Author: Giacomo Guidotto
% Last updated: 2025
% Compiler: pdfLaTeX
% =============================================================================

\documentclass[10pt, a4paper]{article}

% =============================================================================
% PACKAGES
% =============================================================================
% Encoding and fonts
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Layout
\usepackage[margin=1cm]{geometry}
\usepackage{parskip}           % Better paragraph handling than manual \parskip
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}

% Typography
\usepackage{microtype}         % Subtle typographic improvements

% hyperref should be loaded last (with few exceptions)
\usepackage[
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue,
  pdfauthor={Giacomo Guidotto},
  pdftitle={Giacomo Guidotto - Resume},
]{hyperref}

% =============================================================================
% CONFIGURATION
% =============================================================================

% --- Page style ---
\pagestyle{empty}

% --- Lengths (centralized for easy tweaking) ---
\newlength{\sectionspacebefore}
\newlength{\sectionspaceafter}
\newlength{\entryspaceafter}
\newlength{\bulletitemsep}

\setlength{\sectionspacebefore}{8pt}
\setlength{\sectionspaceafter}{4pt}
\setlength{\entryspaceafter}{4pt}
\setlength{\bulletitemsep}{2pt}

% --- List defaults ---
\setlist{
  nosep,
  leftmargin=1.2em,
  topsep=0pt,
  itemsep=\bulletitemsep,
}

% --- Section formatting ---
\titleformat{\section}
{\large\bfseries}  % format
{}                 % label
{0em}              % sep
{}                 % before-code
[\titlerule\vspace{0.2em}]       % after-code

\titlespacing*{\section}
{0pt}                    % left
{\sectionspacebefore}    % before
{\sectionspaceafter}     % after

% =============================================================================
% CUSTOM COMMANDS
% =============================================================================

% --- Header contact item with separator ---
% Usage: \headeritem{content} or \headeritem[url]{content}
\newcommand{\headersep}{\enspace\textbar\enspace}

\newcommand{\headeritem}[2][]{%
  \ifx&#1&%
  #2%
  \else%
  \href{#1}{#2}%
  \fi%
}

% --- Experience entry ---
% Usage: \experience{company}{dates}{role}{location}{bullet items}
\newcommand{\experience}[5]{%
  \noindent
  \textbf{#3}, #1, #4 \hfill #2\par
  \vspace{-0.3em}
  #5
  \vspace{\entryspaceafter}
}

% --- Education entry ---
% Usage: \education{school}{dates}{degree}{location}{bullet items}
\newcommand{\education}[5]{%
  \noindent
  \textbf{#1}, \textit{#2}, #3 \hfill #4\par
  \vspace{-0.3em}
  #5
  \vspace{\entryspaceafter}
  }
  
  % --- Project entry ---
  % Usage: \project{name}{url}{description}
  \newcommand{\project}[3]{%
    #1 \par
    \begin{itemize}
        \vspace{-0.3em}
      \item #2
      \item Repo: \href{#3}{#3}
    \end{itemize}
  \vspace{\entryspaceafter}
}

% --- Skills row ---
% Usage: \skillrow{category}{items}
\newcommand{\skillrow}[2]{\textbf{#1:} & #2 \\}

% =============================================================================
% PERSONAL INFO (edit here)
% =============================================================================
\newcommand{\myname}{Giacomo Guidotto}
\newcommand{\mytitle}{Software Engineer}
\newcommand{\myemail}{xxxxxxxxxxxx@gmail.com}
\newcommand{\myphone}{+39 xxx xxx xxxx}
\newcommand{\mylinkedin}{linkedin.com/in/giacomo-guidotto}
\newcommand{\mygithub}{github.com/giacomoguidotto}

% =============================================================================
% DOCUMENT
% =============================================================================
\begin{document}

% --- Header ---
\begin{center}
  \myphone%
  \headersep%
  \headeritem[mailto:\myemail]{\myemail}%
  \headersep%
  \headeritem[https://\mylinkedin]{\mylinkedin}%
  \headersep%
  \headeritem[https://\mygithub]{\mygithub}
\end{center}

\vspace{2pt}

{\LARGE\bfseries \myname}\par
{\large \mytitle}

% --- About ---
\section{About}

Software Engineer with 3 years at Danfoss, promoted from Junior to Mid in 2 years. Known for high-leverage technical adoption (Next.js, Biome) and fast ramp-up (learned Go and shipped production PRs in <1 week). Experience spans React micro-frontends, Go microservices, Kafka/MQTT integrations, and ML pipelines.

% --- Experience ---
\section{Experience}

\experience
{Danfoss}
{\textit{(Part-time)} Sep 2022 -- Present}
{Software Developer}
{Venice, Italy}
{
Frontend / Micro-frontends (TypeScript, React, Next.js)
\begin{itemize}
    \vspace{-0.4em}
  \item Drove adoption of Next.js on top of React in an incubator (PoC/MVP) setting, enabling a more scalable foundation for production features.
  \item Shipped a new micro-frontend from baseline to production, collaborating across teams on APIs, routing, and shared UI patterns in a micro-frontend architecture.
    \vspace{-0.4em}
\end{itemize}

Backend / Microservices (Go, SQL, Kafka, MQTT)
\begin{itemize}
    \vspace{-0.4em}
  \item Owned a graph-representation microservice end-to-end: researched requirements, designed the data model and APIs, and implemented a sync engine to keep graph/business entities consistent with the database.
  \item Built MQTT client certificate renewal functionality, improving operational reliability for device connectivity.
  \item Optimized Kafka producer path for large payloads via chunking + streaming to reduce memory pressure and improve throughput for big messages.
    \vspace{-0.4em}
\end{itemize}

Data / ML Pipelines (Python, MageAI)
\begin{itemize}
    \vspace{-0.4em}
  \item Contributed to Python data processing pipelines (MageAI) interfacing with a data lake and training ML models used for predictive control of energy consumption across business entities.
    \vspace{-0.3em}
\end{itemize}
Promoted from Junior to Mid-level Engineer in 2 years, leading to increased responsibility and impact.
}

\experience
{Ca' Foscari University of Venice}
{\textit{(Part-time)} Oct 2025 -- Present}
{Scientific Researcher}
{Venice, Italy}
{
  \begin{itemize}
    \item Leading development of a Python library for Physics-Informed Neural Networks (PINNs), focusing on modular architecture
      and strong developer experience.
    \item Reduced training time by $\sim$30\% via novel stopping criteria and training workflow improvements.
      \vspace{-0.4em}
  \end{itemize}
  Tech: Python, PyTorch, PyTorch Lightning, uv, Docker, CI/CD.
}

% --- Education ---
\section{Education}

\education
  {Ca' Foscari University of Venice}
  {BSc in Computer Science}
  {Venice, Italy}
  {\textit{(While working)} Sep 2022 -- Jul 2025}
  {
  \begin{itemize}
    \item \textbf{GPA: 29.0/30}. Research thesis on Physics-Informed Neural Networks for epidemiological modeling.
  \end{itemize}
  }

\education
  {University of Gothenburg}
  {Erasmus Exchange}
  {Gothenburg, Sweden}
  {\textit{(While working)} Sep 2024 -- Jan 2025}
  {
  \begin{itemize}
    \item Relevant coursework: Data Science \& AI, Functional Programming.
    \end{itemize}
  }
    
    % --- Projects ---
    \section{Projects}
    
    \project
    {
      \textbf{PINN:} Modular Physics-Informed Neural Networks framework  (Python, PyTorch Lightning)
    }{
      Framework to solve ODEs and inverse problems by composing physics constraints with configurable weights; supports learnable fields and parameters with reusable components.
    }
    {https://github.com/giacomoguidotto/pinn}

\project
{
  \textbf{Workspace:} Reproducible dev environment + dotfiles (Nix flakes, home-manager, Dotbot)
}{
  Declarative, XDG-compliant development environment using Nix for reproducible, sandboxed setups.
}
{https://github.com/giacomoguidotto/workspace}

% --- Achievements ---
\section{Achievements}

\begin{itemize}
  \item Selected among top 15\% of STEM mentees (2,000+ applicants), LeadTheFuture, 2025.
  \item Selected for summer school on cutting-edge CS research, BOOST '25, 2025.
  \item Cambridge Advanced English (C2), Grade: 203, 2025.
\end{itemize}

% --- Skills ---
% \section{Skills}

% \begin{tabularx}{\textwidth}{@{} l X @{}}
%   \skillrow{Languages}{Italian (Native), English (C2)}
%   \skillrow{Interests}{Live to 100+ years, jumping from airplanes, producing films}
% \end{tabularx}

% --- Footer ---
\vspace{4pt}
\begin{center}
  \footnotesize\textit{I authorize the processing of my personal data pursuant to applicable law.}
\end{center}

\end{document}